Cryptanalysis of \MORUS

### 2018-05-12 morusAC_08_Conclusion.tex
added link to implementation

The results presented here were originally found during the Flexible
Symmetric Cryptography workshop held at the Lorentz Center in Leiden,
Netherlands.  The authors would like to thank Meltem Sonmez Turan who
participated to the initial discussion.  The fifth author was
supported by EPSRC Grant EP/M013472/1.  The fouth and sixth authors
are partially supported by the French Agence Nationale de la Recherche
through the BRUTUS project under Contract ANR-14-CE28-0015.

>>>>

The results presented here were originally found during the Flexible
Symmetric Cryptography workshop held at the Lorentz Center in Leiden,
Netherlands.  The authors would like to thank Meltem Sonmez Turan who
participated in the initial discussion.
The fourth and sixth authors
are partially supported by the French Agence Nationale de la Recherche
through the BRUTUS project under Contract ANR-14-CE28-0015.
The fifth author was supported by EPSRC Grant EP/M013472/1.
